\sffamily \Large Supplementary Information\\[0.1cm] {\bfseries Introspection dynamics in asymmetric multiplayers games}

### 2023-01-23 latex/supplementary.tex
Latex and Notebook changes till 23rd Jan

\newcommand{\A}{\mathbf{A}}
\newcommand{\abf}{\mathbf{a}}
\newcommand{\T}{\mathbf{T}}
\newcommand{\ubf}{\mathbf{u}}

@@

\begin{document}
\maketitle
\onehalfspacing
\section*{The general model for introspection dynamics}
We consider an asymmetric normal form game with $N (>2)$ players. Each player, $i$, has access to their action set, $\A^i$, in which there are $m_i$ possible actions that they can play, $\A^i = \{a^i_i, a^i_2, ..., a^i_{m_i}\}$. The payoff for an individual $i$ depends on what everyone plays and is represented by $\pi^i(\abf^1, \abf^2, ..., \abf^N)$, where $\abf := (\abf^1, \abf^2,...,\abf^N) \in \A^1 \times \A^2 \times ... \times \A^N =: \A$ represents a state of the game. In this model we only consider pure strategies for players. So, player $i$ has only $m_i$ possible strategies. Therefore, the total number of states possible for the game is the product of all $m_i$. 
\\ \\
\noindent We represent a state of the game, $\abf$, from the perspective of player $j$ as $\abf =: (\abf^j, \abf^{-j})$. In the state $(\abf^j, \abf^{-j})$, player $j$ plays the action $\abf^j \in \A^j$ and all the other co-players of $j$ play $\abf^{-j} \in \Pi_{k \neq j} \A^k$. The payoff of player $j$ in this state is also represented as $\pi^j(\abf^j, \abf^{-j})$.
\\ \\
\noindent The players update their strategies over time using the introspection dynamics \cite{couto2022introspection}. At every time step, one randomly chosen player can update their strategy. The randomly chosen player, say $j$, currently playing strategy $a^j_k$, compares their current payoff to the payoff that they would obtain if they played a randomly selected strategy,  $a^j_l \neq a^j_k$, from their action set $\A^j$. This comparison is done while assuming that the co-players do not change from $\abf^{-j}$. Then, they adopt this new strategy  with the probability:

@@

\begin{equation}
 p^j_{a^j_k \to a^j_k} (\abf^{-j}) = 1 - \sum_{k \neq l} p^j_{a^j_k \to a^j_l} (\abf^{-j})
 \label{Eq:introspection-normalization}
\end{equation}
\\ 
\noindent Now, with the help of Eq. \ref{Eq:introspection-update} and \ref{Eq:introspection-normalization}, we can define the transition matrix $\T$ of the process. The transition matrix is a square matrix of size $\Pi_i m_i$. The element $\T_{\abf_p, \abf_q}$ of the matrix represents the probability that the game will go to state $\abf_q$ from state $\abf_p$ in a time step. Before defining the transition matrix, we define the notion of neighbouring states.

@@

\begin{theorem}
When $\beta$ is finite, the unique stationary distribution, $\ubf = (\ubf_\abf)_{\abf \in \A}$, of an N-player additive game under the introspection dynamics is given by: 
\begin{equation}
\ubf_a = \prod_{j=1}^N \frac{1}{\displaystyle \sum_{a' \in \A^j} e^{\beta \left( \pi^j_{a'} -  \pi^j_{\abf^j} \right) }} 
\label{Eq:additive-game-stationary-distribution}
\end{equation}
where, $\pi^j_{a'} - \pi^j_{\abf^j}$ is the co-player independent payoff difference that $j$  earns in an additive game when they switch their play to $a'$ from $\abf^j$ while their co-players do not change their respective plays.
\label{Th:additive-games-stationary-dist}
\end{theorem}

\begin{theorem}
Let $\ubf = (\ubf_\abf)_{\abf \in \A}$ be the unique stationary distribution of an N-player additive game under the introspection dynamics with finite $\beta$. Then, $\ubf_\abf$ is the product of elements of the marginal distributions that correspond to the actions that the players play in state $\abf$. That is,

@@

\noindent and, the marginal $\xi^j_{\abf^j}$ is given by:

\begin{equation}
\xi^j_{\abf_j} = \frac{1}{\displaystyle \sum_{a' \in \A^j} e^{\beta \left( \pi^j_{a'} -  \pi^j_{\abf^j} \right) }} 
\label{Eq:marginal-at-additive-game}
\end{equation}
\noindent where, $\pi^j_{a'} - \pi^j_{\abf^j}$ is the co-player independent payoff difference that $j$  earns in an additive game when they switch their play to $a'$ from $\abf^j$ while their co-players do not change their respective plays.
\label{Th:additive-game-product-of-marginals}
\end{theorem}

\noindent In other words, the above theorem states that for additive games, the frequency that the game will be in state $\abf = (\abf^1, \abf^2, ...,\abf^N)$ under the finite selection introspection dynamics, is the product of the probabilities that the players respectively adopt the action $\abf^j$ which appear in this state $\abf$. \\ \\
\noindent To elucidate this result further, we use an example of a 2-player additive game where each player has three possible actions from the action set $\{\mathit{0},\mathit{1},\mathit{2}\}$. The result says that the expected frequency of the state $(\mathit{0,2})$, say, where player 1 and player 2 simultaneously play $\mathit{0}$ and $\mathit{2}$ respectively: $\ubf_{(\mathit{0,2})}$, is the product of the marginal probabilities that the first player plays $\mathit{0}$ and the second player plays $\mathit{2}$ in the game. That is,

@@

\section*{Examples of multiplayer games and results} 
\subsection*{Linear public goods game}
We consider the linear public goods game with $N$ asymmetric players. Each player has two possible actions, to contribute ($a=1$), or to not contribute ($a=0$). The players differ in their cost of cooperation and their productivities. The cost of cooperation and the productivity of a player $i$ are denoted by $c_i$ and $r_i$.  The payoff for player $i$ when the state of the game is $\abf$ is given by:

\begin{equation}
\pi^i(\abf) = \sum_{j=1}^N \frac{\displaystyle r_j a_j c_j}{N} - a_i c_i
\label{Eq:linear-pgg-payoff}
\end{equation}

\noindent The difference in payoffs between playing the two actions in a linear public goods game is independent of what the other co-players play in the game. That is,

\begin{equation}
\pi^i(\abf^i = 0, \abf^{-i}) - \pi^i(\abf^i = 1, \abf^{-i}) = c_i \left(1 - \frac{r_i}{N} \right) =: f(c_i, r_i) 
\label{Eq:difference-payoffs-lpgg}
\end{equation}

\noindent is independent of $\abf^{-i}$. The linear public goods game is therefore an example of an additive game. This property of the game results in dominated strategies for player $i$ depending on the relationship between their productivity $r_i$ and number of players $N$. When $r_i < N$, the action of not contributing ($a = 0$) dominates the action of contributing ($a = 1$) and vice-versa.

\begin{lemma}
\label{prop:stationary-dist-lpgg}
When $\beta$ is finite, the unique stationary distribution of an asymmetric linear public goods game under introspection dynamics is given by:

\begin{equation}
\ubf_\abf = \prod_{j = 1}^{N} \frac{1}{1 + \displaystyle e^{\mathit{sign}(\abf^j)\beta f(c_j, r_j )}} \quad ,\forall \abf \in \{0,1\}^N
\label{Eq:stationary_dist_lpgg}
\end{equation}
where, 
\begin{equation}
\mathit{sign}(a) = 2a - 1
\end{equation}
\end{lemma}

\section*{Appendix: Proofs}

\begin{proof}
\textbf{Proof of Theorem} \ref{Th:additive-games-stationary-dist} \\ \\ 
Since $\beta$ is finite, the transition matrix of the process $\T$ given by Eq. \ref{Eq:transition-matrix} is primitive and therefore, the stationary distribution $\ubf = (\ubf_\abf)_{\abf \in \A}$ of the row-stochastic transition matrix is unique and satisfies the conditions laid out in Eq. \ref{Eq:lefteigenvector} and \ref{Eq:normalizationcondition}. To continue for the rest of the proof, we introduce some short-cut notation that will be of use later in the proof:\\
\begin{align}
I_{q} &:= I(\abf_q,\abf), \quad \mathit{iff} \quad \abf_q \in \mathit{Neb}(\abf) \\ \notag \\ 
\label{Eq:shortcut-tau}
\tau^j_{\abf^j} &:= \frac{1}{\displaystyle \sum_{a' \in \A^j} e^{\beta \left( \pi^j_{a'} -  \pi^j_{\abf^j} \right) }} 
\end{align}
\noindent In order to show that the candidate stationary distribution, as proposed in Eq. \ref{Eq:additive-game-stationary-distribution} is the stationary distribution of the process, we need to show that the following are true:
\begin{eqnarray}
\label{step-one}
\T_{\abf,\abf} \ubf_a  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} = \ubf_a \quad \forall \abf \in \A \\ 
\label{step-two}
\sum_{\abf \in \A} \ubf_\abf  = 1
\end{eqnarray}
The Eq \ref{step-one} can be simplified further with the steps: 
\begin{align}
&\T_{\abf,\abf} \ubf_a  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} = \\
& \left( 1 - \frac{1}{N} \sum_{\abf_q \in \mathit{Neb}(\abf)} \frac{1}{m^{I_q}-1} \cdot p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \ubf_{\abf} \right) + \sum_{\abf_q \in \mathit{Neb}(\abf)}  \frac{1}{m^{I_q}-1} \cdot p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \ubf_{\abf_q} = \\ \notag \\
\label{eq:important-step}
& \ubf_\abf +  \frac{1}{N} \sum_{\abf_q \in \mathit{Neb}(\abf)} \left( \prod_{k \neq I_q} \tau^k_{\abf^k} \right) \left( p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \tau^{I_q}_{\abf^{I_q}} -  p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \tau^{I_q}_{\abf^{I_q}_q} \right) \cdot \left(  \frac{1}{m^{I_q}-1} \right)
\end{align}
\\ Using the definition of probability of update of the introspection dynamics, as given by Eq. \ref{Eq:introspection-update} and Eq. \ref{Eq:shortcut-tau}, it can be shown that: 
\begin{equation}
p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \tau^{I_q}_{\abf^{I_q}} -  p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \tau^{I_q}_{\abf^{I_q}_q} = 0
\label{important-step-is-zero}
\end{equation}
\\ \noindent Plugging the equality in Eq. \ref{important-step-is-zero} into Eq. \ref{eq:important-step}, we can see that the left hand side of Eq. \ref{step-one} indeed simplifies to $\ubf_{\abf}$. Now, to confirm that the candidate $\ubf$ is the unique stationary distribution we need to check if Eq. \ref{step-two} holds. Simplifying the left hand side of this equation shows that:
\begin{align}
\sum_{\abf \in \A} \ubf_\abf &= \sum_{\abf \in \A} \prod_{k=1}^N \tau^k_{\abf^k} \\ \notag \\
\label{step-prod-sum-sum-prod}
&= \left( \prod_{k=1}^N \sum_{\abf' \in \A} \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \left( \sum_{\abf \in \A} \prod_{k=1}^N \displaystyle e^{\beta \pi^k_{\abf^k}} \right) \\ \notag \\
\label{step-prod-is-one}
&= 1
\end{align}
\noindent The step from Eq. \ref{step-prod-sum-sum-prod} to Eq \ref{step-prod-is-one} is possible because the sum and product in Eq. \ref{step-prod-sum-sum-prod} are interchangeable for both the terms. Therefore, condition Eq. \ref{step-two} is satisfied too. 
\end{proof}

\begin{proof}
\textbf{Proof of Theorem} \ref{Th:additive-game-product-of-marginals} \\ \\ 
If $\ubf$ is the unique stationary distribution of the additive game with $N-$players under finite selection introspection dynamics, it is given by the expression in Eq. \ref{Eq:additive-game-stationary-distribution}. We calculate the marginal distribution of any arbitrary state $\abf$, $\xi_{\abf} = (\xi^j_{\abf^j})_{j = 1,2,...,N}$ by using the definition of marginal distribution in Eq. \ref{Eq:marginal-definition}. It follows that: 
\begin{align}
\xi^j_{\abf^j} &= \sum_{\mathbf{b} \in \A^{-j}} \ubf_{(\abf^j,\mathbf{b})} \\ \notag \\
&= \left( \prod_{k=1}^N \sum_{\abf' \in \A^k} \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \displaystyle e^{\beta \pi^j_{\abf^j}} \cdot \left( \sum_{\mathbf{b} \in \A^{-j}} \prod_{k \neq j} e^{\beta \pi^k_{\mathbf{b}^k}} \right) \\ \notag \\
&= \left( \sum_{\abf' \in \A^j} \displaystyle e^{\beta \pi^j_{\abf'}}\right)^{-1} \cdot \displaystyle e^{\beta \pi^j_{\abf^j}} \cdot \left( \prod_{k\neq j} \sum_{\abf' \in \A^k} \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \left( \sum_{\mathbf{b} \in \A^{-j}} \prod_{k \neq j} e^{\beta \pi^k_{\mathbf{b}^k}} \right) \\ \notag \\ 
&= \left( \sum_{\abf' \in \A^j} \displaystyle e^{\beta \pi^j_{\abf'}}\right)^{-1} \cdot \displaystyle e^{\beta \pi^j_{\abf^j}} \cdot \left( \sum_{\abf' \in \A^{-j}} \prod_{k\neq j}  \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \left( \sum_{\mathbf{b} \in \A^{-j}} \prod_{k \neq j} e^{\beta \pi^k_{\mathbf{b}^k}} \right) \\ \notag \\ 
&= \left( \sum_{\abf' \in \A^j} \displaystyle e^{\beta \left( \pi^j_{\abf'} - \pi^j_{\abf^j}\right)}\right)^{-1}
\end{align}
\noindent Therefore, the marginal distribution follows Eq.  \ref{Eq:marginal-at-additive-game}. Now since we also additionally know that the stationary distribution follows the form Eq. \ref{Eq:additive-game-stationary-distribution}, we can conclude that for additive games, under introspection dynamics with finite selection, Eq. \ref{Eq:additive-game-products} holds. 
\end{proof}

@@

&\bar{\abf}^j := \{0,1\} \setminus \abf^j  \\ 
&p^j := \frac{1}{1 + \displaystyle e^{\beta f(c_j, r_j)}}

@@

&\ubf_a = \T_{\abf,\abf} \ubf_a  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q}  \\ 

@@

When the above decomposition is perfomed $N-1$ more times, the sum of the right hand side becomes 1. This prooves that the candidate stationary distribution is also normalized. 

>>>>

\newcommand{\A}{\mathbf{A}}
\newcommand{\abf}{\mathbf{a}}
\newcommand{\T}{\mathbf{T}}
\newcommand{\ubf}{\mathbf{u}}
\newcommand{\C}{\mathrm{C}}
\newcommand{\D}{\mathrm{D}}

@@

\begin{document}
\maketitle
\onehalfspacing
\section*{The general model for introspection dynamics}
We consider a normal form game with $N (>2)$ players. Each player, $i$, has access to their action set, $\A^i$, in which there are $m^i$ possible actions that they can play, $\A^i = \{a^i_1, a^i_2, ..., a^i_{m^i}\}$. The payoff for an individual $i$ depends on what everyone plays and is represented by $\pi^i(\abf^1, \abf^2, ..., \abf^N)$, where $\abf := (\abf^1, \abf^2,...,\abf^N) \in \A^1 \times \A^2 \times ... \times \A^N =: \A$ represents a state of the game. In this model we only consider pure strategies for players. So, player $i$ has only $m^i$ possible strategies. Therefore, the total number of states possible for the game is the product of all $m^i$. 
\\ \\
\noindent We represent a state of the game, $\abf$, from the perspective of player $j$ as $\abf =: (\abf^j, \abf^{-j})$. In the state $(\abf^j, \abf^{-j})$, player $j$ plays the action $\abf^j \in \A^j$ and all the other co-players of $j$ play $\abf^{-j} \in \Pi_{k \neq j} \A^k$. The payoff of player $j$ in this state is also represented as $\pi^j(\abf^j, \abf^{-j})$.
\\ \\
\noindent The players update their strategies over time using the introspection dynamics \cite{couto2022introspection}. At every time step, one randomly chosen player can update their strategy. The randomly chosen player, say $j$, currently playing strategy $a^j_k$, compares their current payoff to the payoff that they would obtain if they played a randomly selected strategy,  $a^j_l \neq a^j_k$, from their action set $\A^j$. This comparison is done while assuming that the co-players do not change from $\abf^{-j}$. Then, they adopt this new strategy  with the probability:

@@

\begin{equation}
 p^j_{a^j_k \to a^j_k} (\abf^{-j}) = 1 - \sum_{k \neq l} p^j_{a^j_k \to a^j_l} (\abf^{-j})
 \label{Eq:introspection-normalization}
\end{equation}
\\ 
\noindent Now, with the help of Eq. \ref{Eq:introspection-update} and \ref{Eq:introspection-normalization}, we can define the transition matrix $\T$ of the process. The transition matrix is a square matrix of size $M = m^1 \times m^2 \times ... \times m^N$. The element $\T_{\abf_p, \abf_q}$ of the matrix represents the probability that the game will go to state $\abf_q$ from state $\abf_p$ in a time step. Before defining the transition matrix, we define the notion of neighbouring states.

@@

\begin{theorem}
When $\beta$ is finite, the unique stationary distribution, $\ubf = (\ubf_\abf)_{\abf \in \A}$, of the introspection dynamics for the N-player additive game is given by: 
\begin{equation}
\ubf_a = \prod_{j=1}^N \frac{1}{\displaystyle \sum_{a' \in \A^j} e^{\beta \left( \pi^j_{a'} -  \pi^j_{\abf^j} \right) }} 
\label{Eq:additive-game-stationary-distribution}
\end{equation}
where, $\pi^j_{a'} - \pi^j_{\abf^j}$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play to $a'$ from $\abf^j$.
\label{Th:additive-games-stationary-dist}
\end{theorem}
\noindent The above theorem gives a closed form expression of the stationary distribution of the introspection dynamics for additive multiplayer games. For any finite value of the selection parameter, $\beta$, the stationary distribution can be analytically calculated using the expression in Eq. (\ref{Eq:additive-game-stationary-distribution}). The expression is derived by assuming that the update process of the introspection dynamics is governed by Eq. (\ref{Eq:introspection-update}) and (\ref{Eq:introspection-normalization}). For proof, see Appendix \ref{Section:Appendix}.

\begin{theorem}
Let $\ubf = (\ubf_\abf)_{\abf \in \A}$ be the unique stationary distribution of the introspection dynamics with finite $\beta$ for the N-player additive game. Then, $\ubf_\abf$ is the product of the marginal probabilities that each player plays their respective actions in $\abf$. That is,

@@

\noindent where the marginal probability, $\xi^j_{\abf^j}$, is the cumulative probability that player $j$ plays $\abf^j$ at the stationary distribution. The marginal probability is given by:

\begin{equation}
\xi^j_{\abf_j} = \frac{1}{\displaystyle \sum_{a' \in \A^j} e^{\beta \left( \pi^j_{a'} -  \pi^j_{\abf^j} \right) }} 
\label{Eq:marginal-at-additive-game}
\end{equation}
\noindent where, $\pi^j_{a'} - \pi^j_{\abf^j}$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play to $a'$ from $\abf^j$ in an additive game.
\label{Th:additive-game-product-of-marginals}
\end{theorem}

\noindent In other words, the above theorem states for additive games, the probability that the game will be in state $\abf = (\abf^1, \abf^2, ...,\abf^N)$ in the long run (considering a finite selection strength introspection dynamics) is the product of the cumulative probabilities that each player $j$ respectively adopts the action $\abf^j$ in the stationary distribution. \\ \\
\noindent To elucidate this result further, we use an example of a 2-player additive game where each player has three possible actions from the action set $\{\mathit{0},\mathit{1},\mathit{2}\}$. The result says that the expected frequency of the state $(\mathit{0,2})$, say, where player 1 and player 2 simultaneously play $\mathit{0}$ and $\mathit{2}$ respectively: $\ubf_{(\mathit{0,2})}$, is the product of the marginal probabilities that the first player plays $\mathit{0}$ and the second player plays $\mathit{2}$ in the game. That is,

@@

\subsection*{Example of multiplayer additive game: linear public goods game}
We consider the linear public goods game with $N$ asymmetric players. Each player has two possible actions, to contribute (action, $\C$), or to not contribute (action, $\D$). The players differ in their cost of cooperation and their productivities. The cost of cooperation and the productivity of a player $i$ are denoted by $c^i$ and $r^i$.  The payoff for player $i$ when the state of the game is $\abf$ is given by:

\begin{equation}
\pi^i(\abf) = \sum_{j=1}^N \frac{\displaystyle r^j a^j c^j}{N} - a^i c^i
\label{Eq:linear-pgg-payoff}
\end{equation}
\\
\noindent The difference in payoffs between playing the two actions in a linear public goods game is independent of what the other co-players play in the game. That is,

\begin{equation}
\pi^i(\abf^i = \D, \abf^{-i}) - \pi^i(\abf^i = \C, \abf^{-i}) = c^i \left(1 - \frac{r^i}{N} \right) =: f(c^i, r^i) 
\label{Eq:difference-payoffs-lpgg}
\end{equation}
\\
\noindent is independent of $\abf^{-i}$. The linear public goods game is therefore an example of an additive game. This property of the game results in dominated strategies for player $i$ depending on the relationship between their productivity $r^i$ and number of players $N$. When $r^i < N$, the action of not contributing ($\D$) dominates the action of contributing ($\C$) and vice-versa. 
\\
\begin{lemma}
\label{prop:stationary-dist-lpgg}
When $\beta$ is finite, the unique stationary distribution of the introspection dynamics for an asymmetric linear public goods game under introspection dynamics is given by: 
\\
\begin{equation}
\ubf_\abf = \prod_{j = 1}^{N} \frac{1}{1 + \displaystyle e^{\mathit{sign}(\abf^j)\beta f(c^j, r^j )}} \quad ,\forall \abf \in \{\C, \D\}^N
\label{Eq:stationary_dist_lpgg}
\end{equation}
where, 
\begin{equation}
\label{Eq:sign-function}
\mathit{sign}(a) =
\begin{cases}
1& \quad \text{if} \quad a = \C \\
-1& \quad \text{if} \quad a = \D
\end{cases}
\end{equation}
\end{lemma}

\section*{Symmetric multiplayer games with two strategies}

In the previous section we looked at properties of the stationary distribution of the introspection dynamics for additive games. In this section we look at properties of the stationary distribution for any multiplayer game where players are symmetric and have two actions in their action set. A $N-$player symmetric normal form game satisfies the following properties:

\begin{enumerate}
\item $\A^1 = \A^2 = ... = \A^N = \mathcal{A}$, and
\item For any $i, j \in \{1,2,...,N\}, a \in \mathcal{A}$ and $\mathbf{b} \in \displaystyle \prod_{k=1}^{N-1} \mathcal{A}$: 
\begin{equation}
\pi^i(a, \mathbf{b}) = \pi^j(a, \mathbf{b})
\end{equation}
\end{enumerate}

\noindent In addition, when there are only two actions in the action set of players we define the action set in the same way as we did in the section of linear public goods game: $\mathcal{A} := \{\C, \D\}$. Since all players are symmetric in the two-action game, the number of states of the game can be reduced from  $2^N$ to $N+1$. Now, the state $k$ corresponds to $k$ players playing $\C$ and $N-k$ players playing $\D$. For the sake of notational simplicity, we denote the payoffs of a $\C$ and $\D$ player in the state $k$ as $\pi^{\C}(k)$ and $\pi^{\D}(k)$ respectively.

%We define following mapping function:  
%
%\begin{equation}
%e(a^i):= 
%\begin{cases}
%1 \quad \text{if} \quad a^i = a_\C \\
%0 \quad \text{if} \quad a^i = a_\D  
%\end{cases}
%\end{equation}
%\\
%We define $N_\C(\abf)$ as the number of $\C$ players in a state $\abf$. That is, 
%
%\begin{equation}
%N_\C(\abf) := \sum_{i = 1}^N e(\abf^i)
%\end{equation}
%\noindent 
%\\
\begin{lemma}
When $\beta$ is finite, the unique stationary distribution, $(\ubf_k)_{k \in \{0,1,...,N\}}$, of the introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{a_\C, a_\D \}$, is given by:
\begin{equation}
\label{Eq:stationary-dist-symm-2-stgs}
\ubf_k = \frac{1}{T(k)} \cdot {N \choose k} \cdot \displaystyle \prod_{j=0}^{k} \displaystyle e^{\beta f(j-1)}
\end{equation}
where, $f(j) := \pi^\D(k+1) - \pi^\C(k)$ and $T(k)$ is the normalization factor, given by,
\begin{equation}
\label{Eq:normalization-Tk}
T(k) = \displaystyle \sum_{k=0}^N {N \choose k} \cdot \displaystyle \prod_{j=0}^{k} \displaystyle e^{\beta f(j-1)}
\end{equation}
\end{lemma}

\section*{Appendix: Proofs}
\label{Section:Appendix}
\begin{proof}
\textbf{Proof of Theorem} \ref{Th:additive-games-stationary-dist} \\ \\ 
Since $\beta$ is finite, the transition matrix of the process $\T$ given by Eq. \ref{Eq:transition-matrix} is primitive and therefore, the stationary distribution $\ubf = (\ubf_\abf)_{\abf \in \A}$ of the row-stochastic transition matrix is unique and satisfies the conditions laid out in Eq. \ref{Eq:lefteigenvector} and \ref{Eq:normalizationcondition}. To continue for the rest of the proof, we introduce some short-cut notation that will be of use later in the proof:\\
\begin{align}
I_{q} &:= I(\abf_q,\abf), \quad \mathit{iff} \quad \abf_q \in \mathit{Neb}(\abf) \\ \notag \\ 
\label{Eq:shortcut-tau}
\tau^j_{\abf^j} &:= \frac{1}{\displaystyle \sum_{a' \in \A^j} e^{\beta \left( \pi^j_{a'} -  \pi^j_{\abf^j} \right) }} 
\end{align}
\noindent In order to show that the candidate stationary distribution, as proposed in Eq. \ref{Eq:additive-game-stationary-distribution} is the stationary distribution of the process, we need to show that the following are true:
\begin{eqnarray}
\label{step-one}
\T_{\abf,\abf} \ubf_\abf  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q}= \ubf_a \quad \forall \abf \in \A \\ 
\label{step-two}
\sum_{\abf \in \A} \ubf_\abf  = 1
\end{eqnarray}
The Eq \ref{step-one} can be simplified further with the steps: 
\begin{align}
&\T_{\abf,\abf} \ubf_\abf  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q}= \\
& \left( 1 - \frac{1}{N} \sum_{\abf_q \in \mathit{Neb}(\abf)} \frac{1}{m^{I_q}-1} \cdot p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \ubf_{\abf} \right) + \sum_{\abf_q \in \mathit{Neb}(\abf)}  \frac{1}{m^{I_q}-1} \cdot p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \ubf_{\abf_q} = \\ \notag \\
\label{eq:important-step}
& \ubf_\abf +  \frac{1}{N} \sum_{\abf_q \in \mathit{Neb}(\abf)} \left( \prod_{k \neq I_q} \tau^k_{\abf^k} \right) \left( p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \tau^{I_q}_{\abf^{I_q}} -  p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \tau^{I_q}_{\abf^{I_q}_q} \right) \cdot \left(  \frac{1}{m^{I_q}-1} \right)
\end{align}
\\ Using the definition of probability of update of the introspection dynamics, as given by Eq. \ref{Eq:introspection-update} and Eq. \ref{Eq:shortcut-tau}, it can be shown that: 
\begin{equation}
p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \tau^{I_q}_{\abf^{I_q}} -  p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \tau^{I_q}_{\abf^{I_q}_q} = 0
\label{important-step-is-zero}
\end{equation}
\\ \noindent Plugging the equality in Eq. \ref{important-step-is-zero} into Eq. \ref{eq:important-step}, we can see that the left hand side of Eq. \ref{step-one} indeed simplifies to $\ubf_{\abf}$. Now, to confirm that the candidate $\ubf$ is the unique stationary distribution we need to check if Eq. \ref{step-two} holds. Simplifying the left hand side of this equation shows that:
\begin{align}
\sum_{\abf \in \A} \ubf_\abf &= \sum_{\abf \in \A} \prod_{k=1}^N \tau^k_{\abf^k} \\ \notag \\
\label{step-prod-sum-sum-prod}
&= \left( \prod_{k=1}^N \sum_{\abf' \in \A} \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \left( \sum_{\abf \in \A} \prod_{k=1}^N \displaystyle e^{\beta \pi^k_{\abf^k}} \right) \\ \notag \\
\label{step-prod-is-one}
&= 1
\end{align}
\noindent The step from Eq. \ref{step-prod-sum-sum-prod} to Eq \ref{step-prod-is-one} is possible because the sum and product in Eq. \ref{step-prod-sum-sum-prod} are interchangeable for both the terms. Therefore, condition Eq. \ref{step-two} is satisfied too. 
\end{proof}

\begin{proof}
\textbf{Proof of Theorem} \ref{Th:additive-game-product-of-marginals} \\ \\ 
If $\ubf$ is the unique stationary distribution of the $N-$player additive game with under the finite selection introspection dynamics, it is given by the expression in Eq. \ref{Eq:additive-game-stationary-distribution}. We calculate the marginal distribution of any arbitrary state $\abf$, $\xi_{\abf} = (\xi^j_{\abf^j})_{j = 1,2,...,N}$ by using the definition of marginal distribution in Eq. \ref{Eq:marginal-definition}. It follows that: 
\begin{align}
\xi^j_{\abf^j} &= \sum_{\mathbf{b} \in \A^{-j}} \ubf_{(\abf^j,\mathbf{b})} \\ \notag \\
&= \left( \prod_{k=1}^N \sum_{\abf' \in \A^k} \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \displaystyle e^{\beta \pi^j_{\abf^j}} \cdot \left( \sum_{\mathbf{b} \in \A^{-j}} \prod_{k \neq j} e^{\beta \pi^k_{\mathbf{b}^k}} \right) \\ \notag \\
&= \left( \sum_{\abf' \in \A^j} \displaystyle e^{\beta \pi^j_{\abf'}}\right)^{-1} \cdot \displaystyle e^{\beta \pi^j_{\abf^j}} \cdot \left( \prod_{k\neq j} \sum_{\abf' \in \A^k} \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \left( \sum_{\mathbf{b} \in \A^{-j}} \prod_{k \neq j} e^{\beta \pi^k_{\mathbf{b}^k}} \right) \\ \notag \\ 
&= \left( \sum_{\abf' \in \A^j} \displaystyle e^{\beta \pi^j_{\abf'}}\right)^{-1} \cdot \displaystyle e^{\beta \pi^j_{\abf^j}} \cdot \left( \sum_{\abf' \in \A^{-j}} \prod_{k\neq j}  \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \left( \sum_{\mathbf{b} \in \A^{-j}} \prod_{k \neq j} e^{\beta \pi^k_{\mathbf{b}^k}} \right) \\ \notag \\ 
&= \left( \sum_{\abf' \in \A^j} \displaystyle e^{\beta \left( \pi^j_{\abf'} - \pi^j_{\abf^j}\right)}\right)^{-1}
\end{align}
\noindent Therefore, the marginal distribution follows Eq.  \ref{Eq:marginal-at-additive-game}. Now since we also additionally know that the stationary distribution follows the form Eq. \ref{Eq:additive-game-stationary-distribution}, we can conclude that for additive games, under introspection dynamics with finite selection, Eq. \ref{Eq:additive-game-products} holds. 
\end{proof}

@@

&\bar{\abf}^j := \{a_\D,a_\C\} \setminus \abf^j  \\ 
&p^j := \frac{1}{1 + \displaystyle e^{\beta f(c^j, r^j)}}

@@

&\ubf_\abf = \T_{\abf,\abf} \ubf_a  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q}  \\ 

@@

When the above decomposition is perfomed $N-1$ more times, the sum of the right hand side becomes 1. This prooves that the candidate stationary distribution is also a probability distribution.
